\chapter*{Introduction}
This booklet shows how to use the JavaScript library JSXGraph for dynamic mathematics 
(\url{http://jsxgraph.org}).
JSXGraph runs on every modern browser, and on most systems from desktop computers to mobile phones.
The claim of JSXGraph is to be the fastest and the most dynamic library for this purpose.


\marginnote{Dynamic Mathematics, plotting, visualization}

JSXGraph is a cross-browser library for interactive geometry, function plotting, charting, and data visualization in a web browser. 
It is implemented completely in JavaScript, does not rely on any other library, and uses SVG and VML. 
JSXGraph is easy to embed and has a small footprint: 
less than 100 KByte if embedded in a web page. No plug-ins are required! Special care has been taken to optimize the performance. 
Starting with version 0.80 JSXGraph supports multitouch devices like the Apple iPhone and devices running 
Opera mini or Mozilla Fennec.

JSXGraph is developed at the Lehrstuhl f\"ur Mathematik und ihre Didaktik, University of Bayreuth, Germany.


\paragraph{Features}\marginnote{Available at \url{http://jsxgraph.org}}
\begin{itemize}
    \item Euclidean Geometry: Points, lines, circles, intersections, perpendicular lines, angles
    \item  Curve plotting: Graphs, parametric curves, polar curves, data plots
    \item  Turtle graphics
    \item  Lindenmayer systems
    \item  Interaction via sliders
    \item  Animations
    \item  Polynomial interpolation, spline interpolation
    \item  Tangents, normals
    \item  Charts
    \item  Vectors
\end{itemize}

\paragraph{Technical details}
On all browsers except the Internet Explorer JSXGraph uses the vector graphic language SVG. On the Internet Explorer
the vector graphics language VML is used. JSXGraph is highly optimized to run smoothly on all types of browsers. This is true even 
for devices with less computing power like mobile phones.\marginnote{SVG: Scalable Vector Graphics, VML: Vector Markup Language}



\paragraph{License}

JSXGraph is released under the LGPL - Lesser GNU General Public License. So, everybody is encouraged to use it.
